A Tidy Framework and Infrastructure to Systematically Assemble Spatio-temporal Indexes from Multivariate Data

### 2023-07-31 tidyindex.qmd
Update Intro paragraph 5

To be able to test different decision choices systematically for an index, the index needs to be broken down into its fundamental building blocks to analyse the contribution and effect of each component. Such decomposition of index components provides the means to standardise index construction via a pipeline and offers benefits for comparing among indexes and calculating index uncertainty. In social indexes for instance, the OECD handbook [@oecd_handbook_2008] has provided a set of steps and recommendations for constructing composite socio-economic indexes. However, there is still a need to extend these guidelines and methods to accommodate the inclusion of more methodological complex steps required for indexes in general.

@@

The rest of the paper is structured as follows: @sec-pipeline reviews the concept of data pipeline in R. The pipeline framework for index construction is presented in @sec-index-pipeline. @sec-dev explains how to include a new building block in each pipeline module. Examples are given in @sec-examples to demonstrate the index construction with the pipeline built.

>>>>

To be able to test different decision choices systematically for an index, the index needs to be broken down into its fundamental building blocks to analyse the contribution and effect of each component. We call this process of breaking the index construction into different steps the index pipeline.  Such decomposition of index components provides the means to standardise index construction via a pipeline and offers benefits for comparing among indexes and calculating index uncertainty. In social indexes for instance, the OECD handbook [@oecd_handbook_2008] has provided a set of steps and recommendations for constructing composite socio-economic indexes. However, there is still a need to extend these guidelines and methods to accommodate the inclusion of more methodological complex steps required for indexes in general.

@@

The rest of the paper is structured as follows: @sec-pipeline reviews the concept of data pipeline in R. The pipeline framework for index construction is presented in @sec-index-pipeline. @sec-dev explains how to add new steps into the index methodology in the form of new building blocks inside the index construction pipeline. Examples are given in @sec-examples to demonstrate the index construction with the pipeline built.
